 

### 2021-06-30 vertical-thermal-review.Rmd
knit in new leaf energy balance figure, deleted older copies
#6
Update vertical-thermal-review.Rmd

Relative humidity, $RH$, tends to be higher in the understory and decrease with height across the vertical profile, although this trend is absent in open forests [Figs. `r fig_NEON_vertical`f, `r SIfig_NEON_all`, e.g., @mcgregor_tree_nodate].
Dense-canopy forests maintain higher daily maximum $RH$ below-canopy than open forests and nearby open areas, and this effect is greater in wetter conditions, and warmer months [@vonarxSpatiotemporalEffectsForest2012a]. 
In combination with $T_{air}$, $RH$ determines vapor pressure deficit ($VPD$) -- the driving force of water loss from leaves, which tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b]. Maximum $T_{air} and VPD in the understory are further decreased with increasing canopy height and LAI [@juckerCanopyStructureTopography2018]. *( This last sentence needs work.)*

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the elevation of $T_{leaf}$ above $T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra*) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Appendix `r appendix_tealeaves_methods`. [ISSUE #6](https://github.com/EcoClimLab/vertical-thermal-review/issues/6).](leaf_energy_balance/Updated T_leaf_png.png)

>>>>

Relative humidity, $RH$, tends to be higher in the understory and decrease with height across the vertical profile, although this trend is absent in open forests [Figs. `r fig_NEON_vertical`f, `r SIfig_NEON_all`, e.g., @mcgregor_tree_nodate].
Dense-canopy forests maintain higher daily maximum $RH$ below-canopy than open forests and nearby open areas, and this effect is greater in wetter conditions, and warmer months [@vonarxSpatiotemporalEffectsForest2012a]. 
In combination with $T_{air}$, $RH$ determines vapor pressure deficit ($VPD$) -- the driving force of water loss from leaves, which tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b]. Maximum $T_{air}$ and VPD in the understory are further decreased with increasing canopy height and LAI [@juckerCanopyStructureTopography2018]. *( This last sentence needs work.)*

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the elevation of $T_{leaf}$ above $T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra*) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Appendix `r appendix_tealeaves_methods`. [ISSUE #6](https://github.com/EcoClimLab/vertical-thermal-review/issues/6).](leaf_energy_balance/leaf_energy_fig3.png)
